A theoretical analysis of the Keep Network random beacon using agent based modeling \\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2019-10-28 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
fixed issue with missing coloumn
added hypergeometric to analytical group selection

\section{Verification and Validation}
Benchmark using analytical methods - from Promethea

@@

\newpage
\section{Conclusion and Future work}
This theoretical analysis highlighted possible behaviors of the Keep network beacon. we
validated the model using some simple analytical methods. However, once the beacon launches
we can use real data from the network to validate and adjust the model. At this point we can
then use the model to better investigate future behaviours and causes of behavior.

\bibliographystyle{plain}
\bibliography{Simulation_paper.bib}

>>>>

\section{Verification and Validation}
Where possible, we use analytical methods to verify aspects of the sim. In the absence of 
real world data, this is our best way to increase confidence in simulation results.

\subsection{Group Selection}
We model group selection using a hypergeometric distribution. For our purposes, we assume the n draws to 
be the equivalent of selecting a group of n members, with k members being malicious. We draw the sample from
a population of N virtual stakers, with K stakers being malicious.

\begin{equation}
    Pr(X = k) = \frac{{K \choose k} {N-K\choose n-k}}{{N \choose n}}
\end{equation}

Show analytical results in comparison with simulation

@@

\section{Conclusion and Future work}
This theoretical analysis highlighted possible behaviors of the Keep network beacon. we
validated the model using some simple analytical methods. However, once the beacon launches
we can use real data from the network to validate and adjust the model. At this point we can
then use the model to better investigate future behaviours and causes of behavior.

\newpage
\bibliographystyle{plain}
\bibliography{Simulation_paper.bib}
